Deterministic Scheduling of Periodic Messages in a Network by a SDN (deterministic) approach

### 2017-07-20 infocom/infocom.tex
avant merge

\begin{abstract}
A recent trend in mobile networks is to centralize the processing units which were attached to 
antennas in distant data-centers. The main challenge is to guarantee that the latency of the periodic messages 
sent from the antennas to their processing units and back is minimal. We show that traditional statistical multiplexing
is bad at ensuring a low latency. Hence, we propose in this article to use a deterministic scheme which allows to send periodic messages without collisions in the network and thus without buffering and additional latency.
We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
Some algorithm solves the problem when the routes are small or the load is small. Whe the parameters are unconstrained,
and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
The experimental results shows that even under full load, most of the time PMLS finds a sending scheme with no latency.
\end{abstract}

>>>>

\begin{abstract}
A recent trend in mobile networks is to centralize the processing units which were attached to 
antennas in distant data-centers. The main challenge is to guarantee that the latency of the periodic messages 
sent from the antennas to their processing units and back is minimal. We show that traditional statistical multiplexing
is bad at ensuring a low latency. Hence, we propose in this article to use a deterministic scheme which allows to send periodic messages without collisions in the network and thus without buffering and additional latency.
We give several algorithms to compute such schemes for a common topology where one link is shared by all antennas.
Some algorithm solves the problem when the routes are small or the load is small. When the parameters are unconstrained,
and some buffering is allowed in the processing units, we propose an algorithm (PMLS) adapted from a classical scheduling method.
The experimental results shows that even under full load, most of the time PMLS finds a sending scheme with no latency.
\end{abstract}
